### 2019-08-13 Thesis/pages/evaluation.tex
Changes; - Typos - Centered diagrams and papers

Further more, comparison of these results to similar literature show a huge increase in success rates for the attack present in this paper. All alternative literature used a small dictionary of around 1024 words. This, therefore, is highly suggestive that the issue lies with the design of Trustwords as present in the Trustword dictionary are multiple homophones and obscure and unpronounceable words. Therefore, we believe that 4 Trustwords as a minimum has not provided a basic level of security towards users.

@@

Research Question \ref{goal:phoneticSimilarity} asks: \textit{``What are the different ways phonetic similarity can be quantified?''}. This paper has discussed a number of metrics used to quantify phonetic similarly (See Section \ref{sec:metrics}). Most metrics were chosen due to their high utilization and occurrence in literature. The only exception to this is the presence of Phonetic Vectors that were chosen due to their unique qualities. This project has succeeded in presenting a comparison of ways to compare similarity metrics. A more in-depth comparison of all possible metrics is a substantial task and would require a project solely dedicated to this task.

\section{Research Question \ref{goal:bestMetrics}}
Research Question \ref{goal:bestMetrics} asks: \textit{``Out of a chosen set of metrics, which are the most effective?''}. 
The paper has presented the performance of a suite of algorithms that are mostly present in utilization and alternative literature. Performance of these metrics were quantified in a direct study that reduced the number down for 5 to 3. These newly selected metrics were then assessed in an attack context with their performance being indirectly quantified. From the historical set of metrics Levenshtein was the best performer with participants rating its matches as substantial better. Levenshtein was also the best performer in the attack context with it having a better average attack success rate that the alternative metrics. This, therefore, this work seems to corroborate work showing that words that are spelt in similar ways tend to share phonetic similarity \cite{hettiarachchi2012sparcl}. This area, however, will require further work to provide more conclusive results on the most effective ways to quantify phonetic similarity.

\section{Research Question \ref{goal:complexity}}
Research Question \ref{goal:complexity}: \textit{``What is the time and computation complexity required to generate a ’similar’ keys for a targeted key pair?''} has been discussed by the project, the actual generation of keys was shown in Section \ref{sec:key_gen} where actual keys were generated. Further more the distribution of key permutations on a set of real-world keys were discussed in Section \ref{sec:averagePerms} and \ref{sec:vulnKeys}. To achieve this the tool GreenOnion was developed where inspiration was gathered from a currently available tool known as Scallion. Experimentation results were gathered and displayed in Section \ref{sec:SvG} that showed the significant increase in the number of near-collision key GreenOnion can test for.

>>>>

Further more, comparison of these results to similar literature show a huge increase in success rates for the attack present in this paper. All alternative literature used a small dictionary of around 1024 words. This, therefore, is highly suggestive that the issue lies with the design of Trustwords. Therefore, we believe that 4 Trustwords as a minimum has not provided a basic level of security towards users.

@@

Research Question \ref{goal:phoneticSimilarity} asks: \textit{``What are the different ways phonetic similarity can be quantified?''}. This paper has discussed a number of metrics used to quantify phonetic similarity (See Section \ref{sec:metrics}). Most metrics were chosen due to their high utilization and occurrence in literature. The only exception to this is the presence of Phonetic Vectors that were chosen due to their unique qualities. This project has succeeded in presenting a comparison of ways to compare similarity metrics. A more in-depth comparison of all possible metrics is a substantial task and would require a project with this sole dedication.

\section{Research Question \ref{goal:bestMetrics}}
Research Question \ref{goal:bestMetrics} asks: \textit{``Out of a chosen set of metrics, which are the most effective?''}. 
The paper has presented the performance of a suite of algorithms that are mostly present in alternative literature. Performance of these metrics were quantified in a direct study that selected the top three from a set of five. These newly selected metrics were then assessed in an attack context with their performance being indirectly quantified. From the historical set of metrics Levenshtein was the best performer with participants rating its matches as substantially better. Levenshtein was also the best performer in the attack context with it having the best average attack success rate. This, therefore, seems to corroborate work showing that words with similar spelling tend to share phonetic similarity \cite{hettiarachchi2012sparcl}. This area, however, will require further work to provide more conclusive results on the most effective ways to quantify phonetic similarity.

\section{Research Question \ref{goal:complexity}}
Research Question \ref{goal:complexity}: \textit{``What is the time and computation complexity required to generate a ’similar’ keys for a targeted key pair?''} has been discussed by the project, the actual generation of keys was shown in Section \ref{sec:key_gen} where actual keys were generated. Further more the distribution of key permutations on a set of real-world keys were discussed in Section \ref{sec:averagePerms} and \ref{sec:vulnKeys}. To achieve this the tool GreenOnion was developed where inspiration was gathered from a currently available tool known as Scallion. Experimentation results were gathered and displayed in Section \ref{sec:SvG} that showed the significant increase in the number of near-collision keys GreenOnion can test for.

\todo{Give some tasty stats}
